SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-09-11 scipy-1.0/paper.tex
Add standard references and timeline from 1.0 ann

@@

The scientific Python ecosystem includes many examples
of domain-specific software libraries building on top
of SciPy features, and then returning to the base SciPy library
to suggest and even implement improvements to enable
more effective science applications. For example, there
are common contributors to the SciPy and astropy core
libraries\cite{astropy-2018}, and what works well for 
one of the code bases, infrastructures, or communities 
is often transferred in some form to the other.

>>>>

\cite{dubois2007guest}
\cite{oliphant2007python}
\cite{perez2007ipython}
\cite{hunter2007matplotlib}
\cite{vanderwalt2008scipy}
\cite{peterson2009f2py}
\cite{millman2011python}
\cite{perez2011python}
\cite{vanderwalt2011numpy}
\cite{behnel2011cython}
\cite{pedregosa2011scikit}
\cite{vanderwalt2014scikit}
\cite{millman2014developing}
\cite{meurer2017sympy}

\begin{figure}
\begin{verbatim}
    2001: first SciPy release
    2005: transition to NumPy
    2007: creation of scikits
    2008: spatial module and first Cython code added
    2010: move to a 6-monthly release cycle
    2011: development moves to GitHub
    2011: Python 3 support
    2012: add a sparse graph module and unified optimization interface
    2012: remove of maxentropy
    2013: continuous integration with TravisCI
    2015: adding Cython interface for BLAS/LAPACK and a benchmark suite
    2017: add a unified C API with LowLevelCallable; remove weave
    2017: SciPy 1.0 release
\end{verbatim}
\caption{Timeline}
\end{figure}

@@

The scientific Python ecosystem includes many examples
of domain-specific software libraries building on top
of SciPy features, and then returning to the base SciPy library
to suggest and even implement improvements to enable
more effective science applications. For example, there
are common contributors to the SciPy and astropy core
libraries\cite{astropy-2018}, and what works well for 
one of the code bases, infrastructures, or communities 
is often transferred in some form to the other. At the code
base level, the \texttt{binned\_statistic} functionality
is one such cross-project contribution---it was initially
developed in an Astropy-affiliated package
and then placed in SciPy after the fact.
